### 2022-06-15 sections/conferences-full.tex
Update conferences-full.tex

\begin{benumerate}{71}

@@

\item{\small González-Bustamante, B. (2022). {\itshape Time-Dependent Data Encoding and Time-Varying Exposure Survival Models to Study Presidential Crises}. Presentation delivered at the R User Conference 2022, Virtual.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2015). {\itshape Media Consumption and Political Participation in Argentina, Chile, and Uruguay}. Presentation delivered at the XII Argentinian Congress of Political Science, Mendoza, Argentina.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2013). {\itshape Trajectories and Patterns of the Ministers' Political Careers in Chile}. Presentation delivered at the XI Argentinian Congress of Political Science, Parana, Argentina.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Twitter as Public Opinion Measure: The Bachelet's Arrival to the Chilean Presidential Campaign 2013}. Presentation delivered at the XI Argentinian Congress of Political Science, Parana, Argentina.}\vspace{1mm}

>>>>

\begin{benumerate}{72}

%% \item{González-Bustamante, B., \& Aguilar, D. (2022). {\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Local Governments}. Presentation delivered at the International Political Science Association Seminar Smart Cities and Open Government: Local Responses to Participation, Public Information, and Democracy, Madrid.}\vspace{1mm}

\item{\small González-Bustamante, B. (2022). {\itshape Quantitative Methods for Studying Elites: Practical Applications, Biases and Potential}. Presentation delivered at the XI Latin American Congress of Political Science, Virtual.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2022). {\itshape Time-Dependent Data Encoding and Time-Varying Exposure Survival Models to Study Presidential Crises}. Presentation delivered at the R User Annual Conference, Virtual.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2015). {\itshape Media Consumption and Political Participation in Argentina, Chile, and Uruguay}. Presentation delivered at the XII Argentine Congress of Political Science, Mendoza, Argentina.}\vspace{1mm}

@@

\item{\small González-Bustamante, B. (2013). {\itshape Trajectories and Patterns of the Ministers' Political Careers in Chile}. Presentation delivered at the XI Argentine Congress of Political Science, Parana, Argentina.}\vspace{1mm}

\item{\small González-Bustamante, B. (2013). {\itshape Twitter as Public Opinion Measure: The Bachelet's Arrival to the Chilean Presidential Campaign 2013}. Presentation delivered at the XI Argentine Congress of Political Science, Parana, Argentina.}\vspace{1mm}
